Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-11 index.Rmd
added link to slides

--
[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~$ Preregistration](https://osf.io/rpu98)

@@

[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~$ Open materials](https://osf.io/6vze3)

@@

[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~$ Open data](https://osf.io/b527v/)

@@

[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)

@@

[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~$ osf.io/vedb4](https://osf.io/vedb4)

@@

[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)

>>>>

--
[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~~$ Preregistration](https://osf.io/rpu98)

@@

[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~~$ Open materials](https://osf.io/6vze3)

@@

[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~~$ Open data](https://osf.io/b527v/)

@@

[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)

@@

[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~~$ osf.io/vedb4](https://osf.io/vedb4)

@@

[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)

[`r icon_style(icons::fontawesome("tv"), scale = 1.7, fill = "#035AA6")` $~~$ Slides at bit.ly/many-analysts](https://bit.ly/many-analysts)
